Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-25 LaTeX_paper/paper.tex
finish typo fixes

\subsection{Context}
This section will provide some basic knowledge
related to the jigsaw problem that will be useful
  for the next sections.
\subsubsection{Classification}
Puzzles are categorized in different types, for example 
\begin{itemize}
  \item Type 1 puzzles have the orientation of the pieces known, but the position unknown. 
  \item Type 2 puzzles have both the orientation and the position of the pieces unknown.
  \item Type 3 puzzles have the orientation of the pieces unknown, but the position is known.
\end{itemize}
Between these categories type 2 are the hardest, and will be the focus of this paper.

@@

A puzzle solver program can be divided into 3 sub algorithms,
The Splitter, The Comparator and The Solver.
This generalization can be applied not only to our solution,
but also to all the algorithms analyzed in the related
work section of this paper~\cref{document:related_work}.

@@

	To answer this question we will measure the accuracy of the comparator we developed
  to answer the previous question and observe what would happen if that accuracy is
  applied to a digital puzzle solver. We will then propose a solution to improve
  the accuracy of real-world Comparators.

@@

@@

\subsection{Difference In Execution Time}

This section measures the execution time of many puzzles,
and plots the results. The puzzles that has been used for
this test has been described in ~\cref{document:dataset}.

@@

Looking at the data we can spot to anomalies:
\begin{itemize}
  \item The 4x5 real puzzle has a lower execution time than the 4x4 real puzzle. This is not a big
  difference and can be attribute to run to run variation.
  \item The 8x12 digital puzzle has a much higher execution time than the 16x16 digital puzzle.
  This is also easily explainable, as puzzles whose side is not a power of two are in general
  harder compared to those who fulfill this condition. As they require an extra step compared to
  the simple algorithm shown in section REF.
\end{itemize}

@@

Comparing the results achieved by our algorithm with some of the algorithms seen in the related
work section (\cref{document:related_work}), clearly shows how our algorithm is far away
from the current state of the art digital puzzle solvers. In this section we want to
see if it is possible to use our comparator with current state of the art algorithms.
In particular we selected the ``Graph Connection Laplacian'' solution, due to the
comprehensive details provided in the paper. Notably, it contains information
regarding the algorithm's accuracy in relation to the corruption rate,
which is crucial for this analysis.

@@

Improving the comparator can shortly be done.
Some minor improvements can be made by spending some time
tweaking the current algorithm.
However, it is evident that for a task of this nature,
the most viable solution would likely involve
leveraging machine learning techniques.

But this presents a significant challenge: manually testing if certain
pieces fit together, followed by scanning them and labeling,
is a time-intensive process that could require hundreds,
if not thousands, of hours.

However we just created a puzzle solver, even with a suboptimal
time complexity, can easily solve small size real world puzzles.
We could use it to solve a couple hundred small size puzzles,
and automatically label the results for us,
paving the way to a superior machine learning based comparator.

@@

Furthermore, we have developed a highly effective labeling tool,
which holds great promise for future applications in creating a
machine learning-based comparator. Such a comparator has the potential
to greatly facilitate puzzle-solving algorithms by providing more
accurate data.

>>>>

\subsection{Context}
This section will provide some basic knowledge
related to the jigsaw problem that will be useful
  for the next sections.
\subsubsection{Classification}
Puzzles are categorized in different types, for example 
\begin{itemize}
  \item Type 1 puzzles have the orientation of the pieces known, but the position unknown. 
  \item Type 2 puzzles have both the orientation and the position of the pieces unknown.
  \item Type 3 puzzles have the orientation of the pieces unknown, but the position known.
\end{itemize}
Between these categories type 2 are the hardest, and will be the focus of this paper.

@@

A puzzle solver program can be divided into 3 sub algorithms,
The Splitter, The Comparator and The Solver.
This generalization can be applied not only to our solution,
but also to all the algorithms analyzed in the related
work section of this paper (\cref{document:related_work}).

@@

	To answer this question we will measure the accuracy of the comparator we developed
  and observe what would happen if that accuracy is
  applied to a digital puzzle solver. We will then propose a solution to improve
  the accuracy of real-world Comparators.

@@

This section will describe the implementation of the puzzle solver we developed.
This solver will then be put to the test in the next section.

@@

\subsection{Execution Time Analysis}

This section measures the execution time of many puzzles,
and shows the results. The puzzles that has been used for
this test has been described in ~\cref{document:dataset}.

@@

Looking at the data we can spot to anomalies:
\begin{itemize}
  \item The 4x5 real puzzle has a lower execution time than the 4x4 real puzzle. This is not a big
  difference and can be attribute to run to run variation.
  \item The 8x12 digital puzzle has a much higher execution time than the 16x16 digital puzzle.
  This is also easily explainable, as puzzles whose side is not a power of two are in general
  harder compared to those who fulfill this condition. As they require an extra step compared to
  the simple algorithm shown in~\cref{document:my_solver}.
\end{itemize}

@@

Comparing the results achieved by our algorithm with some of the algorithms seen in the related
work section (\cref{document:related_work}), clearly shows how our algorithm is far away
from the current state-of-the-art digital puzzle solvers. In this section we want to
see if it is possible to use our comparator with current state-of-the-art algorithms.
In particular we selected the ``Graph Connection Laplacian''~\cite{GCL} solution, due to the
comprehensive details provided in the paper. Notably, it contains information
regarding the algorithm's accuracy in relation to the corruption rate,
which is crucial for this analysis.

@@

Some minor improvements to the comparator can be made by spending some time
tweaking the current algorithm.
However, it is evident that for a task of this nature,
the most viable solution would likely involve
leveraging machine-learning techniques.

But this presents a significant challenge: manually testing if certain
pieces fit together, followed by scanning and labeling them,
is a time-intensive process that could require hundreds,
if not thousands, of hours.

However we just created a puzzle solver that, even with a suboptimal
time complexity, can easily solve small size real world puzzles.
We could use it to solve a couple hundred small size puzzles,
and automatically label the results for us,
paving the way to a superior machine learning based comparator.

@@

Furthermore, we have developed a highly effective labeling tool,
which holds great promise for future applications in creating a
machine-learning-based comparator. Such a comparator has the potential
to greatly facilitate puzzle-solving algorithms by providing more
accurate data.
